Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-16 paper/paper.tex

\begin{figure}[htb] 
\centering
\includegraphics[width=1.0\columnwidth]{figures/CYBERSHAKE-Pareto}
\caption{Comparison of DPDS and AW-DPDS algorithms for ensembles of
 100 Pareto-distributed Cybershake workflows}
\label{fig:CYBERSHAKE.n.1000.8.dagh1-20m0}
\end{figure}

>>>>

\begin{figure*}[htb] 
\centering
\includegraphics[width=1.0\textwidth]{figures/MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Comparison of DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows}
\label{fig:}
\end{figure*}

\begin{figure*}[htb] 
\centering
\includegraphics[width=1.0\textwidth]{figures/score-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/score-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/score-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/score-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/score-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Comparison of DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows. Score is computed as $\sum(1/(p+1))$ where
priorities of subsequent workflows are $p=0,1,2,\ldots$ (0 means highest
priority).}
\label{fig:}
\end{figure*}

\begin{figure*}[htb] 
\centering
\includegraphics[width=1.0\textwidth]{figures/score2-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/score2-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/score2-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/score2-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/score2-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Comparison of DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows. Score is computed as $\sum(2^(-p))$ where
priorities of subsequent workflows are $p=0,1,2,\ldots$ (0 means highest
priority).}
\label{fig:}
\end{figure*}

\begin{figure*}[htb] 
\centering
\includegraphics[width=1.0\textwidth]{figures/size-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/size-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/size-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/size-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/size-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Comparison of DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows. Score is equal to the total work completed,
i.e. it is sum of runtimes (in hours) of tasks of completed workflows.}
\label{fig:}
\end{figure*}

\begin{figure*}[htb] 
\centering
\includegraphics[width=1.0\textwidth]{figures/cost-MONTAGE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/cost-CYBERSHAKE-n-1000-8-dagh1-20m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/cost-LIGO-n-1000-8-dagh1-40m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/cost-GENOME-n-1000-8-dagh100-1500m0.pdf}
\includegraphics[width=1.0\textwidth]{figures/cost-SIPHT-n-1000-8-dagh5-50m0.pdf}
\caption{Comparison of DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows. Plot shows effective computing cost in \$ per
hour calclated by dividing sum of task runtimes by the total budget. Higher
cost results from lower resource utilization.}
\label{fig:}
\end{figure*}
